# (PART\*) SRA ON AnVIL {-}


```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Quick Start

In this module, we'll bring some metagenomic data into AnVIL.

This data comes from [this BioProject](https://www.ncbi.nlm.nih.gov/bioproject/PRJNA904247), which collected soil samples to study bacterial communities in tallgrass prairie. Bacteria play an important role in this ecosystem, but can be changed by disturbance, management, and the presence of herbivores.

The SRA Data corresponding to this project is located [here](https://www.ncbi.nlm.nih.gov/Traces/study/?acc=SRP409181&o=acc_s%3Aa).

## Clone

Clone the Workspace `https://anvil.terra.bio/#workspaces/anvil-outreach/SRA-data-on-AnVIL`.

For this demo, we have given the cloned Workspace the name `SRA-data-on-AnVIL`.

## Launch Workflow

Navigate to the WORKFLOWS Tab and select the SRA_Fetch Workflow.

```{r, fig.align='center', echo = FALSE, fig.alt= "Workflows tab with SRA_Fetch.", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g1f25a933000_0_0")
```

Select "Run workflow(s) with inputs defined by data table".

```{r, fig.align='center', echo = FALSE, fig.alt= "'Run workflow(s) with inputs defined by data table' has been selected.", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g1f25a933000_0_10")
```

Set the "Select root entity type" to "sample" and click "SELECT DATA".

```{r, fig.align='center', echo = FALSE, fig.alt= "Step 1 and 2 for setting up the Workflow.", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_0")
```

On the Select Data popup, select only the first sample, `SRR22375322`.

```{r, fig.align='center', echo = FALSE, fig.alt= "The first sample selected from the data table.", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_8")
```

Click on the space underneath "Attribute" and select `this.sample_id`.

```{r, fig.align='center', echo = FALSE, fig.alt= "'this.sample_id' must be selected under the Workflow Attribute", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_17")
```

Click "SAVE".

```{r, fig.align='center', echo = FALSE, fig.alt= "The SAVE button is highlighted", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_26")
```

You are ready to launch the Workflow! Click "RUN ANALYSIS".

```{r, fig.align='center', echo = FALSE, fig.alt= "The RUN ANALYSIS button is highlighted", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_34")
```

Voilà! Your Workflow is running. 

Because the Workflow is happening in the cloud, you can close your browser or shut down your computer without interrupting the transfer.

```{r, fig.align='center', echo = FALSE, fig.alt= "The Workflow status page describes submission statistics and job status", out.width = '100%'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1l0P0gFpsPkYG7blqJ_5JyYYlztJFZDD39CnIB4svrY8/edit#slide=id.g208af248fb0_0_42")
```

